Open-Vocabulary Semantic Parsing\\with both Distributional Statistics and Formal Knowledge

### 2016-03-18 papers/acl2016/paper.tex

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms.  This produced 2.1m predicate
instances involving 142k entity pairs and 184k entities.  After
removing infrequently-seen predicates (seen fewer than 6 times), there
were 25k categories and 4.2k relations.  The differences in numbers
reported here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.

@@

There is a large body of other work that is closely related to what is
presented in this paper.  Two recent papers that also attempt to
include some form of structured knowledge into distributional
representations are those by Faruqui et
al.~\shortcite{faruqui-2015-retrofitting-word-vectors}, and by
Rockt\"{a}schel et
al.~\shortcite{rocktaschel-2015-logical-embeddings}.  A key difference
between their approaches and ours is that they use the structured
information only to modify distributional representations, while we
include the structured information directly in our models, training
weights for structured information jointly with distributional
representations.  Also conceptually similar is the Additive Relational
Effects model for knowledge base completion by Nickel et
al.~\shortcite{nickel-2014-are}, which tries to factorize the residual
of a KB tensor that cannot be explained by observable features that
are somewhat similar to the formal features we use in this model.  But
while this model is conceptually similar, it is computationally quite
different, and would be rather difficult to use in the setting we
explore in this work.

Our work draws a lot of inspiration from recent work on knowledge base
completion.  We are building on top of work in embedding the entities
and relations in a knowledge
base~\cite{riedel-2013-mf-universal-schema,nickel-2011-rescal,bordes-2013-transe},
as well as work on graph-based methods for reasoning with knowledge
bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,neelakantan-2015-rnn-kbc}.

Lastly, there is an extensive literature on building semantic parsers
to answer questions against a structured knowledge
base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing}.
The vast majority of this work is focused on matching natural language
text to statements in a specific ontology, with no hope of assigning
meaning to language that falls outside of that ontology.  Only very
recently has there been work attempting to learn broad coverage
meaning representations in semantic parsers.  In addition to the work
by Krishnamurthy and Mitchell which we extend in this paper, there was
recently a nice piece of work by Choi et
al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies}.  The
aim of their work is, like typical semantic parsers, to map text onto
a single formal statement, but they allow some of the predicates to be
``open'' predicates not contained in the Freebase ontology.  A key
difference between their work and ours is that we score surface
logical forms directly, using a weighted combination of many Freebase
queries, instead of trying to map them to a single Freebase logical
form.  Additionally, while their system might learn that
``front-runner'' should be modeled as an open predicate that has no
representation in Freebase, they have no method to assign any further
meaning to that predicate, while our models learn both distributional
and formal information about the meaning of ``front-runner''.

>>>>

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms~\cite{krishnamurthy-2014-joint-ccg}.
This produced 2.1m predicate instances involving 142k entity pairs and
184k entities.  After removing infrequently-seen predicates (seen
fewer than 6 times), there were 25k categories and 4.2k relations.
The differences in numbers reported here versus those reported by
Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.

@@

In addition to the work described in \secref{background}, there are
three broad classes of work that are related to what we have presented
in this paper.

The first line of research that our work is related to is knowledge
base completion.  In addition to SFE~\cite{gardner-2015-sfe}, our work
draws inspiration from work on embedding the entities and relations in
a knowledge base~\cite{riedel-2013-mf-universal-schema,%
nickel-2011-rescal,bordes-2013-transe,nickel-2014-are,%
toutanova-2015-joint-text-kb-embedding}, as well as work on
graph-based methods for reasoning with knowledge
bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,%
neelakantan-2015-rnn-kbc}.

Second, our work is conceptually related to many methods that aim to
learn word embeddings that are informed by some kind of external
knowledge~\cite{faruqui-2015-retrofitting-word-vectors,%
rocktaschel-2015-logical-embeddings,schwartz-2016-symmetric-patterns-w2v,%
yu-2014-w2v-with-semantic-knowledge}.
A key difference between these approaches and ours is that they use
the structured information only to modify distributional
representations, while we include the structured information directly
in our models, training weights for structured information jointly
with distributional representations.

Lastly, there is an extensive literature on building semantic parsers
to answer questions against a structured knowledge
base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing,%
li-2015-semantic-parsing-scfg}.  The vast majority of this work is
focused on matching natural language text to statements in a specific
schema, with no hope of assigning meaning to language that falls
outside of that schema.  Only very recently has there been work
attempting to learn broad coverage meaning representations in semantic
parsers.  In addition to the work by Krishnamurthy and Mitchell
discussed in \secref{background}, and work by Lewis and
Steedman~\shortcite{lewis-2013-combined-distributional-and-logical-semantics}
which Krishnamurthy and Mitchell extended, Choi et
al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies},
extended a traditional semantic parser with the notion of ``open''
predicates not contained in the Freebase ontology.  A key difference
between their work and ours is that, while their system might learn
that ``front-runner'' should be modeled as an open predicate that has
no representation in Freebase, they have no method to assign any
further meaning to that predicate, whereas our models learn both
distributional and formal information about the meaning of
``front-runner''.
